Clean_Condition_Survival

### 2023-06-09 smelt_2019_allseasons/clean_conditionfactor_survival.Rmd

```{r}
library(tidyverse)
library(lubridate)
library(readr)
root <- "smelt_2019_allseasons"
```

@@

# Condition Factor, Length, Weight
1. Read data
```{r}
summerdata <- read_csv("smelt_2019_allseasons/Raw_Smelt-Length-Weight_Summer2019.csv", col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
  rename(K0 = K) 
falldata <- read_csv("smelt_2019_allseasons/Raw_Smelt-Length-Weight_Fall2019.csv", col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
  rename(K0 = K)

winterspringdata <- read_csv("smelt_2019_allseasons/Cagetype_data.csv") %>%
  rename(Pre_FL=Pre_FL_cm,
         Post_FL=Post_FL_cm,
         Pre_Weight=Pre_Weight_g,
         Post_Weight=Post_Weight_g)
```

2. Reformat
```{r}
winspring_long <- winterspringdata %>% 
  select(-Delta_CF, -X1) %>%
  pivot_longer(cols = c(Pre_FL:Post_CF),
               names_to = c("Period", ".value"),
               names_sep = "_")

# Filter to only large mesh and RV
winspring_clean <- winspring_long %>%
  filter(Site != "DWSC",
         Mesh == "large") %>%
  rename(FL_cm = FL,
         Weight_g = Weight,
         K0 = CF) %>%
  mutate(Deployment = ifelse(Site =="DWSC", "Spring",
                             ifelse(Site == "RV", "Winter", NA )),
         ID = NA,
         ID = as.character(ID),
         Deployment = as.factor(Deployment),
         Period = as.factor(Period),
         Site = as.factor(Site),
         Cage = as.factor(Cage))%>%
  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage)

summerfall_clean <- rbind(summerdata, falldata) %>%
  mutate(FL_mm = replace(FL_mm, FL_mm == "-", NA),
         FL_mm = as.numeric(FL_mm),
         FL_mm = FL_mm/10, na.rm = TRUE) %>%
  rename(FL_cm = FL_mm) %>%
  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage)

>>>>

```{r}
library(tidyverse)
library(lubridate)
library(readr)
library(here)
root <- "smelt_2019_allseasons"
```

@@

# Condition Factor, Length, Weight
1. Read data
```{r}
summerdata <- read_csv(here(root,"data_raw","Raw_Smelt-Length-Weight_Summer2019.csv"), col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
  rename(K0 = K) %>%
  mutate(Season = "Summer")

falldata <- read_csv(here::here(root,"data_raw", "Raw_Smelt-Length-Weight_Fall2019.csv"), col_types = cols(Deployment = "f", Period = "f", Site = "f", ID = "c", FL_mm = "c", Weight_g= "d", Cage = "f", K =  "d", Comments =  "c")) %>%
  rename(K0 = K) %>%
  mutate(Season = "Fall")

winterspringdata <- read_csv(here(root, "data_raw", "Cagetype_data.csv")) %>%
  rename(Pre_FL=Pre_FL_cm,
         Post_FL=Post_FL_cm,
         Pre_Weight=Pre_Weight_g,
         Post_Weight=Post_Weight_g) %>%
  mutate(Season = "Winter",
         ID = paste0("Winter_",`...1`))
```

2. Reformat
```{r}
winspring_long <- winterspringdata %>% 
  select(-Delta_CF, -`...1`) %>%
  pivot_longer(cols = c(Pre_FL:Post_CF),
               names_to = c("Period", ".value"),
               names_sep = "_")

# Filter to only large mesh and RV
winspring_clean <- winspring_long %>%
  rename(FL_cm = FL,
         Weight_g = Weight,
         K0 = CF) %>%
  mutate(Deployment = "Winter",
         Deployment = as.factor(Deployment),
         Period = as.factor(Period),
         Site = as.factor(Site),
         Cage = as.factor(Cage))%>%
  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage, Season)

summerfall_clean <- rbind(summerdata, falldata) %>%
  mutate(FL_mm = replace(FL_mm, FL_mm == "-", NA),
         FL_mm = as.numeric(FL_mm),
         FL_mm = FL_mm/10, na.rm = TRUE) %>%
  rename(FL_cm = FL_mm) %>%
  select(Deployment, Period, Site, ID, FL_cm, Weight_g, Cage, Season)
